### 2022-07-28 main/chapter_2ljets.tex
weaken too honest complaint

Numerical simplicity is valuable.
In internal documentation, I stated that it was a motivator behind the design,
but that statement was removed after one \atlas\ author commented:
``maybe this paragraph is a little
\emph{too honest}? (The `numerical simplicity' bit)''
(emphasis added)~\cite{comment2020toohonest}.

>>>>

Numerical simplicity is valuable.
I wrote in a draft of our \atlas-internal documentation that numerical
simplicity was a design goal, but am guilty of removing that statement after a
senior reviewer suggested that it was ``too honest''.
% ~\cite{comment2020toohonest}. % Could cite, probably should not.
